Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
wrote nmore about makespan and memory usage on normal cluster

    \subsubsection{Static experiments}
    \paragraph{Memory-constrained cluster}

@@

    \paragraph{Normal cluster}

    On a normal cluster, the baseline \heft had $24.2\%$ success rate ($75.7\%$ failure rate).
    All the heuristics could schedule all workflows. \skug{check this tomorrow for two weird failures}.

    Figure~\ref{fig:ms-relations} shows the relations of the makespans foound by the heuristics to the makespans found by the baseline.
    On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline, the makespans of \heftblc are $8\%$
    worse, and those found by \heftmm are $71\%$ worse.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/MsRelations2}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.}
        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow size. Smaller is better.}
        \label{fig:ms-relations-by-workflow}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
        \caption{Memory usage by algorithm by workflow size. Includes invalid heft schedules}
        \label{fig:mem-usages}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/success-rates-large}
        \caption{Success rates on the \skug{normal} cluster.}
        \label{fig:success-rates-large}
        \vspace{-0.3cm}
    \end{figure}

>>>>

    \subsubsection{Static experiments}

    \skug{TODO for all pictures: substitute 0 in sizes through <100. Will be done in one commit for all.}
    \paragraph{Normal cluster}

    On a normal cluster,  all three of our heuristics were able to schedule all workflows(Figure~\ref{fig:success-rates-large}).
    The baseline \heft had $24.2\%$ success rate ($75.7\%$ failure rate).
    It was able to schedule preliminarily small workflows, with no workflows over the size of $4000$ tasks being scheduled
    correctly.
    Small workflows are less constrained by the memory requirement, so in the situation of abundant processing resources, even
    a not memory-aware approach is able to produce valid schedules.
    However, this advantage quickly vanishes as workflows grow larger.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=0.9\columnwidth] {images/success-rates-large}
        \caption{Success rates on the \skug{normal} cluster.}
        \label{fig:success-rates-large}
        \vspace{-0.3cm}
    \end{figure}

    Figure~\ref{fig:ms-relations-by-workflow} shows the relations of the makespans found by the heuristics to the
    makespans found by the baseline (including invalid ones), by workflow size.
    On average, the makespans found by \heftbl are $7.8\%$ worse than those found by the baseline, the makespans of \heftblc are $8\%$
    worse, and those found by \heftmm are $82.6\%$ worse.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/MsRelations2}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline. Smaller is better.
        \skug{SUGESTION: remove this picture, as it duplicates Fig 3}
        }

        \label{fig:ms-relations}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/makespan_relations_by_wf_size}
        \caption{Relative makespans produced by the heuristics to the makespan produced by the baseline, by workflow
        size. Smaller is better. \skug{CHECK this pictue. It might have a wrong mean function}}
        \label{fig:ms-relations-by-workflow}
        \vspace{-0.3cm}
    \end{figure}

    The percentage of memory occupied by the schedule is another its important characteristic.
    Fig.~\ref{fig:mem-usages-normal} shows the percentage of memory occupied on average by the schedule produced by different
    algorithms, by workflow size.

    \heftmm continuously outperforms other heuristics in memory usage, using from $46\%$ less memory on the smallest
    workflows to $4$ times less memory on the largest \numprint{30000}-task workflows.
    If we consider the invalid \heft schedules, too, we see that they would require more and more memory on average.
    This is because some assignments require more that $100\%$ of memory (which makes them invalid).
    We can assess the degree of invalidity by comparing \heft memory usage with the memory usage of \heftbl.
    \heftbl differs from the baseline only in the sense that it respects available memory on the processors.
    For the largest workflows, \heft schedules require almost double the memory of \heftbl.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-normal}
        \caption{Memory usage by algorithm by workflow size. Includes invalid heft schedules}
        \label{fig:mem-usages-normal}
        \vspace{-0.3cm}
    \end{figure}

    Figure~\ref{fig:mem-usages-onlyvalid} shows memory usages if only valid heft schedules are presented.
    There are no valid heft scheduler from middle-sized and large workflows, so no red bars are present.

@@
